Informative Autonomous Sampling of Oceanographic Variables Using Joint Excursion Sets

### 2019-10-10 main_new.tex
updates

\begin{abstract}
  Improving and optimizing oceanographic sampling is a crucial task
  for marine science and maritime management. Faced with limited
  resources to understand dynamic processes in the water-column, the
  combination of statistics and autonomous robotics provide new
  opportunities for studying experimental design. In this work we develop
  methods for efficient spatial sampling applied to the mapping of
  coastal processes by providing informative descriptions of spatial
  characteristics of ocean phenomena. Specifically, we define a design
  criterion based on reducing uncertainty in the joint excursions of
  random fields, and derive analytical expressions for the expected
  Bernoulli variance reduction in the excursion set of spatial
  temperature and salinity variables, providing a description of
the boundary uncertainty that can be used to prioritize sampling efforts at locations that are
ambiguous, making exploration more effective. We show how these can be
  applicable in static and sequential designs, building on myopic and
  non-myopic sampling strategies. We use simulations to study the
  properties and differences between state-of-the-art approaches,
  followed by results from field deployments with an autonomous
  underwater vehicle as part of a case study mapping the boundary of a
  river plume. The results demonstrate the potential of combining statistical methods and robotic platforms, and the abilities of the derived methods to effectively inform and execute data-driven environmental sampling.

>>>>

\begin{abstract}
  Improving and optimizing oceanographic sampling is a crucial task
  for marine science and maritime management. Faced with limited
  resources to understand dynamic processes in the water-column, the
  combination of statistics and autonomous robotics provide new
  opportunities for studying experimental design. In this work we
  develop methods for efficient spatial sampling applied to the
  mapping of coastal processes by providing informative descriptions
  of spatial characteristics of ocean phenomena. \kc{Specifically, we
    define a design criterion based on reducing uncertainty in the
    joint excursions of random fields, and derive analytical
    expressions for the expected Bernoulli variance reduction in the
    excursion set of spatial temperature and salinity variables,
    providing a description of the boundary uncertainty that can be
    used to prioritize sampling efforts at locations that are
    ambiguous, making exploration more effective ---- TOO LONG. Break
    it up}. We show how these can be applicable in static and
  sequential designs, building on myopic and non-myopic sampling
  strategies. We use simulations to study the properties and
  differences between state-of-the-art approaches, followed by results
  from field deployments with an autonomous underwater vehicle as part
  of a case study mapping the boundary of a river plume. The results
  demonstrate the potential of combining statistical methods and
  robotic platforms, and the abilities of the derived methods to
  effectively inform and execute data-driven environmental sampling.
